---
title: "R Notebook"
output: html_notebook
---
 
# Setup 

```{r, setup}
wd <- "C:\\Users\\heinr\\OneDrive\\Desktop\\LARGE DATA\\LinkedIn\\Write-up"
opts_knit$set(root.dir = wd)

library(knitr)


```

# Preview Data

### Individual profile descriptions
```{r}
read.csv(file = '../company_level_individual_profiles/24-hour-fitness_person_profile_50_word_cutoff.csv')
```
Individual descriptions are in company files... What about duplicates?


### Individual employment duration by company
```{r}
read.csv(file = '../company_level_individual_stay_term/24-hour-fitness_person_stay_term.csv')
```
These are in separate files divided by company

### Company metadata
```{r}
read.csv(file = 'company_level_info_with_grouped_sector.csv')
```
Everything in one file 

### LIWC scores 
```{r}
read.csv(file = 'LIWC_idividual_company_mapped.csv', nrows = 1000)
```
I do not think I have the x files ... 
x = individuals 
y = companies


### Company-individual LIWC similarity scores
```{r}
read.csv(file = 'LIWC_idividual_company_mapped_similarity.csv', nrows = 1000)
```
Again, I do not think I have the x files ... 
x = individuals 
y = companies

### Company LIWC scores 
```{r}
read.csv(file = 'LIWC2015_Company.csv', nrows = 1000)
```

### Individual LIWC scores 
```{r}
read.csv(file = 'LIWC2015_Individual1.csv', nrows = 1000)
```


```{r}
read.csv(file = 'LIWC2015_Individual2.csv', nrows = 1000)
```

```{r}
read.csv(file = 'LIWC2015_Individual3.csv', nrows = 1000)
```
Cant find the individual files 
Why are these in three dfs? Size?


### Merged emplyment duration and distance metrics
```{r}
read.csv(file = 'stay_term_and_distances.csv', nrows = 1000)
```
Probably makes sense to split indices ... 
Are person ids really unique? 
