---
title: "LinkedIn_analysis"
output: html_document
---

```{r setup, include=FALSE}

wd <- "C:\\Users\\heinr\\OneDrive\\Desktop\\LARGE DATA\\LinkedIn\\Write-up"
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = wd)

library(tidyverse)
library(lmerTest)
source('functions.R')
```

# Read data
```{r message=FALSE, warning=FALSE}
df_dist_liwc <- read_csv('../full_files_csv/df_dist_liwc.csv')
df_diff_liwc <- read_csv('../full_files_csv/df_diff_liwc.csv')
df_dist_wemb <- read_csv('../full_files_csv/df_dist_wemb.csv')
df_stay_term <- read_csv('../full_files_csv/df_stay_term.csv')
```

# Merge data
### LIWC distance measures 
```{r}
df_dist_liwc_clean <- df_dist_liwc %>% select(-X, -company, -Filename.x)

df_dist_liwc_merged <- plyr::join(df_stay_term, df_dist_liwc_clean, 
                                  by=c('comp_id', 'person_id'),
                                  type='inner')
```

### LIWC component scores
```{r}
df_diff_liwc_clean <- df_diff_liwc %>% select(-X, -company, -Filename.x)

df_diff_liwc_merged <- plyr::join(df_stay_term, df_diff_liwc_clean, 
                                  by=c('comp_id', 'person_id'),
                                  type='inner')
```

### Word embedding distance measures
```{r}
df_dist_wemb_clean <- df_dist_wemb %>% select(-X, -org_profile_link,
                                              -parent_folder, -batch_folder, 
                                              -given_name, -family_name, 
                                              -header_title, -header_location)

df_dist_wemb_merged <- plyr::join(df_stay_term, df_dist_wemb_clean, 
                                  by=c('comp_id', 'person_id'),
                                  type='inner')
```

### Check for missing companies
```{r}
comps_liwc = df_dist_liwc %>% select(comp_id) %>% unique() %>% as.vector()
comps_wemb = df_dist_wemb %>% select(comp_id) %>% unique() %>% as.vector()

setdiff(comps_wemb, comps_liwc)
setdiff(comps_liwc, comps_wemb)
        
write_csv(setdiff(comps_wemb, comps_liwc), 'liwc_missing_comps.csv')
```


# Further preprocessing
### Filtering
```{r}
df_dist_liwc_merged_clean <- df_dist_liwc_merged %>% 
  filter(is_current_job == F) %>%
  mutate(n_months = log(n_months+1))

df_diff_liwc_merged_clean <- df_diff_liwc_merged %>% 
  filter(is_current_job == F) %>%
  mutate(n_months = log(n_months+1))

df_dist_wemb_merged_clean <- df_dist_wemb_merged %>% 
  filter(is_current_job == F) %>%
  mutate(n_months = log(n_months+1))
```

### Scaling
```{r}
df_dist_liwc_merged_comp <- df_dist_liwc_merged_clean %>%
  group_by(comp_id) %>%
  mutate_at(vars(n_months, cos_dist, euc_dist, manh_dist, 
                 iforest_ad, ocsvm_ad, sos_ad), scale) %>%
  ungroup()

df_diff_liwc_merged_comp <- df_diff_liwc_merged_clean %>%
  group_by(comp_id) %>%
  mutate_if(is.numeric, scale) %>%
  ungroup()

df_dist_wemb_merged_comp <- df_dist_wemb_merged_clean %>%
  group_by(comp_id) %>%
  mutate_at(vars(n_months, cos_dist, euc_dist, manh_dist,
                 iforest_ad, ocsvm_ad, sos_ad), scale) %>%
  ungroup()
```

### Drop individuals with insuficient number of jobs
```{r}
person_ids_liwc_dist <- df_dist_liwc_merged_clean %>% 
  group_by(person_id) %>% 
  summarize(n = n()) %>% 
  filter(n > 3) %>% 
  .$person_id

person_ids_liwc_diff <- df_dist_liwc_merged_clean %>% 
  group_by(person_id) %>% 
  summarize(n = n()) %>% 
  filter(n > 3) %>% 
  .$person_id

person_ids_wemb <- df_dist_wemb_merged_clean %>% 
  group_by(person_id) %>% 
  summarize(n = n()) %>% 
  filter(n > 3) %>% 
  .$person_id
```

```{r}
df_dist_liwc_merged_pers <- df_dist_liwc_merged_clean %>%
  filter(person_id %in% person_ids_liwc_dist) %>%
  group_by(person_id) %>%
  mutate_at(vars(n_months, cos_dist, euc_dist, manh_dist,
                 iforest_ad, ocsvm_ad, sos_ad), scale) %>%
  ungroup()

df_diff_liwc_merged_pers <- df_diff_liwc_merged_clean %>%
  filter(person_id %in% person_ids_liwc_diff) %>%
  group_by(person_id) %>%
  mutate_if(is.numeric, scale) %>%
  ungroup()

df_dist_wemb_merged_pers <- df_dist_wemb_merged_clean %>%
  filter(person_id %in% person_ids_wemb) %>%
  group_by(person_id) %>%
  mutate_at(vars(n_months, cos_dist, euc_dist, manh_dist,
                 iforest_ad, ocsvm_ad, sos_ad), scale) %>%
  ungroup()
```

```{r}
df_dist_liwc_merged_cross <- df_dist_liwc_merged_clean %>%
  filter(person_id %in% person_ids_liwc_dist) %>%
  mutate_at(vars(n_months, cos_dist, euc_dist, manh_dist,
                 iforest_ad, ocsvm_ad, sos_ad), scale)

df_diff_liwc_merged_cross <- df_diff_liwc_merged_clean %>%
  filter(person_id %in% person_ids_liwc_diff) %>%
  mutate_if(is.numeric, scale) %>%
  ungroup()

df_dist_wemb_merged_cross <- df_dist_wemb_merged_clean %>%
  filter(person_id %in% person_ids_wemb) %>%
  mutate_at(vars(n_months, cos_dist, euc_dist, manh_dist,
                 iforest_ad, ocsvm_ad, sos_ad), scale)
```


# Analysis 
## LIWC distance metrics
### Nested within companies
```{r}
results_liwc_comp <- run_mlm(df_dist_liwc_merged_comp, 
                             y = 'n_months', nesting = 'company')

mlm_aggregator(results_liwc_comp)
```

### Nested within person 
```{r}
results_liwc_pers <- run_mlm(df_dist_liwc_merged_pers, 
                             y = 'n_months', nesting = 'person')

mlm_aggregator(results_liwc_pers)
```


### Crossed person x company
```{r}
# results_liwc_cross <- run_mlm(df_dist_liwc_merged_cross, 
#                              y = 'n_months', nesting = 'crossed')

# mlm_aggregator(results_liwc_cross)
```


## Word embedding distance metrics
### Nested within companies
```{r}
results_wemb_comp <- run_mlm(df_dist_wemb_merged_comp, 
                             y = 'n_months', nesting = 'company')

mlm_aggregator(results_wemb_comp)
```

### Nested within person 
```{r}
results_wemb_pers <- run_mlm(df_dist_wemb_merged_pers, 
                             y = 'n_months', nesting = 'person')

mlm_aggregator(results_wemb_pers)
```

### Crossed person x company
```{r}
# results_wemb_cross <- run_mlm(df_dist_wemb_merged_cross, 
#                              y = 'n_months', nesting = 'crossed')

# mlm_aggregator(results_liwc_cross)
```

## LIWC component scores WORK
### Nested within companies
```{r}
mlm_work_comp <- lmer(n_months ~ diff_work.x + (diff_work.x||comp_id), 
                         data = df_diff_liwc_merged_comp)

summary(mlm_work_comp)
```
```{r}
mlm_work_comp <- lmer(n_months ~ abs(diff_work.x) +
                        (abs(diff_work.x)||comp_id), 
                         data = df_diff_liwc_merged_comp)

summary(mlm_work_comp)
```

### Nested within person 
```{r}
mlm_work_pers <- lmer(n_months ~ diff_work.x + (diff_work.x||person_id), 
                         data = df_diff_liwc_merged_pers)

summary(mlm_work_pers)
```
```{r}
mlm_work_pers <- lmer(n_months ~ abs(diff_work.x) + 
                        (abs(diff_work.x)||person_id), 
                         data = df_diff_liwc_merged_pers)

summary(mlm_work_pers)
```



## LIWC component scores LEISURE
### Nested within companies
```{r}
mlm_leisure_comp <- lmer(n_months ~ abs(diff_leisure.x) + 
                           (abs(diff_leisure.x)||comp_id), 
                         data = df_diff_liwc_merged_comp)

summary(mlm_leisure_comp)
```

### Nested within person 
```{r}
mlm_leisure_pers <- lmer(n_months ~ abs(diff_leisure.x) + 
                           (abs(diff_leisure.x)||person_id), 
                         data = df_diff_liwc_merged_pers)

summary(mlm_leisure_pers)
```


